--- 
lang: "pt-br"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
classoption: openany
fontsize: 12pt
linestretch: 1.5
geometry: "left=3.5cm,right=2cm,top=3cm,bottom=3cm, asymmetric"
toc: true
toc-depth: 2
toc-title: Índice
lof: True
lot: True
description: "Thesis carried out within the scope of the master's degree in statistics,
  mathematics and computing from Universidade Aberta."
---

# Prerequisites {-}

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

Exemplo
